Adaptive evolution with aneuploidy and mutation

### 2022-01-26 ms/ms.tex
revise fig S1 caption, added fig S1 todos

% Fig Curveball 
\begin{figure}[h]
	\centering
	% generated with growth_curves.ipynb and deg = '39' 
	\includegraphics[width=0.45\textwidth]{../figures/evo39_fitness_39deg.pdf}
	% generated with growth_curves.ipynb and deg = '30' 
	\includegraphics[width=0.45\textwidth]{../figures/evo39_fitness_30deg.pdf}
	% generated with growth_curves_refined.ipynb and deg = '30' 
	\includegraphics[width=0.45\textwidth]{../figures/refined_vs_evo39_fitness_39deg.pdf}
\caption{
    \textbf{Fitness estimation from growth curves.}
    \textbf{(A)} Fitness estimation from growth curves collected at \SI{39}{\celsius}. Mean: 1.024; 95\% CI: 0.959 - 1.115.
    \textbf{(B)} Fitness estimation from growth curves collected at \SI{30}{\celsius}. Mean: 0.986;  95\% CI: 0.979 - 0.994.
    \textbf{(C)} Fitness estimation from growth curves collected at \SI{39}{\celsius}. Mean: 1.033; 95\% CI: 1.027 - 1.041.
    \\
    Growth curves previously described in \citet[Figs. 3C, 4A, and S2]{Yona2012}.
	Fitness estimated from growth curves using \texttt{Curveball}, a method for predicting results of competition experiments from growth curve data~\citep[\href{https://curveball.yoavram.com}{curveball.yoavram.com}]{Ram2019}. See \emph{Models and Methods, Prior distributions} for more details.
} 
\label{fig:growth-curves}
\end{figure}

>>>>

% Fig Curveball 
\begin{figure}[h]
	\centering
	% generated with growth_curves.ipynb and deg = '39' 
	\includegraphics[width=0.45\textwidth]{../figures/evo39_fitness_39deg.pdf} \\
	% generated with growth_curves.ipynb and deg = '30' 
	\includegraphics[width=0.45\textwidth]{../figures/evo39_fitness_30deg.pdf} \\
	% generated with growth_curves_refined.ipynb and deg = '30' 
	\includegraphics[width=0.45\textwidth]{../figures/refined_vs_evo39_fitness_39deg.pdf}
\caption{
    \textbf{Fitness estimation from growth curves.}
    % you need to give each panel a label so that you will have A-L; have A-D on same row, then E-H same row, I-L on same row;
    % caption should explain what each panel shows.
    \textbf{(A)} Fitness estimation from growth curves of \euwt\ and \anwt\ at \SI{39}{\celsius}: $\hat w_{2n+1}/w_{2n}$=1.024 (95\% CI: 0.959 - 1.115).
    \textbf{(B)} Fitness estimation from growth curves of \euwt\ and \anwt\ at \SI{30}{\celsius}: $\hat w_{2n+1}/w_{2n}$= 0.986 (95\% CI: 0.979 - 0.994).
    \textbf{(C)} Fitness estimation from growth curves of \anwt\ and \eumt\ at \SI{39}{\celsius}: $\hat w_{2n*}/w_{2n+1}$=1.033 (95\% CI: 1.027 - 1.041).
    Growth curves previously described in \citet[Figs. 3C, 4A, and S2]{Yona2012}.
	Fitness estimated from growth curves using \texttt{Curveball}, a method for predicting results of competition experiments from growth curve data~\citep[\href{https://curveball.yoavram.com}{curveball.yoavram.com}]{Ram2019}. See \emph{Models and Methods, Prior distributions} for more details.
} 
\label{fig:growth-curves}
\end{figure}
